\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel-space

### 2012-05-16 conclusion.tex
write conclusion; fix intro

@@

% TODO write this for real
And lo, the Author did{\s}t pre{\s}ent Land{\s}lide to yon re{\s}earch Community, and to the {\s}tudents of XV-CDX as well. Verily, the Kernel developers young and olde found Bugges of Concurren{\s}y in their code. The {\s}oftware then{\s}eforth worked as Intended, cra{\s}hing nevermore, and there was much rejoicing.

>>>>

\revision{
Systematic exploration is a powerful technique for exposing race conditions in concurrent systems.
%It is more reliable than stress testing, and able to find more diverse types of bugs than data race detection.
In previous research, systematic exploration has proven useful in user-level and distributed systems, yet a gap stands between the technique and the complex world of kernel-level concurrency debugging. In this thesis, we present techniques for bridging this gap.

We have built Landslide, a tool for performing systematic exploration in kernel space with a focus on Pebbles kernels written for 15-410. We showed that Landslide's techniques make systematic exploration in kernel space both possible and efficient, and that Landslide can help students find bugs in their own kernels.

With Landslide, we see testing a kernel as a process of manipulating test parameters in two ways: first, in the choice of test case, and second, in the user's configuration of Landslide to express which parts of the kernel are ``interesting'' and which are irrelevant.
Finding and understanding race conditions exposed by a given test becomes a joint effort between the user and Landslide, combining the user's knowledge about the kernel's design and Landslide's ability to explore many interleavings efficiently.

Our work on Landslide has indicated many possible avenues for continued work on systematic exploration in kernel space. We see potential for Landslide to be a useful debugging tool both for students of 15-410 and for developers of general purpose operating systems. Application to mainstream kernels also opens up the possibility to apply systematic testing techniques to device driver code, known for being prone to concurrency errors.
Finally, the current emphasis on user-guided steering of test parameters suggests long-running testing approaches which could automate a user's intuition for how to find meaningful results quickly.

We hope that the ideas presented here serve as stepping stones to develop more sophisticated systematic debugging techniques for kernel-level race conditions.
}

@@

\begin{quote}
\em
And lo, the Author did{\s}t pre{\s}ent Land{\s}lide to yon re{\s}earch Community, and to the {\s}tudents of XV-CDX as well. Verily, the Kernel developers young and olde found Bugges of Concurren{\s}y in their code. The {\s}oftware then{\s}eforth worked as Intended, cra{\s}hing nevermore, and there was much rejoicing.
\end{quote}

### 2012-05-16 thesis.tex
write conclusion; fix intro

We present Landslide,\footnote{
Landslide {\em (n)}: a phenomenon which demonstrates that Pebbles are not as stable as you might think.}
a tool for applying systematic race detection techniques in to kernel-level code.
It is geared towards kernels that implement the Pebbles specification, the main project in Operating System Design and Implementation (15-410) at CMU, and is implemented as a module for Wind River Simics\textsuperscript{\texttrademark}\cite{simics}, the x86 simulator that students use to run their Pebbles kernels.
During execution of a kernel, Landslide records important actions performed by the kernel, attempts to decide at which points in the kernel's execution a preemption will be most likely to expose a bug, and then exercises all possible interleavings of kernel threads around such points.
When Landslide finds a bug (predicted by a set of common checks and heuristics), it stops execution and prints information about the sequence of interleavings that exposed the bug.

With Landslide, we see testing a kernel as a process of manipulating test parameters in two ways: first, in the choice of test case (the user-space program that exercises a specific set of system calls), and second, in the configuration of Landslide in regard to which parts of the kernel are ``interesting'' in the behaviour of the test case and which are irrelevant.
Searching for and understanding race conditions exposed by a given test becomes a joint effort between the programmer and Landslide, combining the programmer's specific knowledge about the design of the kernel and Landslide's ability to explore many interleavings efficiently.

>>>>

We present Landslide,\footnote{
Landslide {\em (n)}: a phenomenon which demonstrates that Pebbles are not as stable as you might think.}
a tool for applying systematic race detection techniques in to kernel-level code.
It is geared towards kernels that implement the Pebbles specification, the main project in Operating System Design and Implementation (15-410) at CMU, and is implemented as a module for Wind River Simics\textsuperscript{\texttrademark}\cite{simics}, the x86 simulator that students use to run their Pebbles kernels.
\revision{In order to use Landslide, a kernel programmer must instrument their kernel to inform Landslide of important concurrency events during the execution, and configure Landslide to focus its search on components of the kernel most relevant to the test.
%During a kernel's execution, Landslide records important actions performed by the kernel, decides at which points in the kernel's execution a preemption will be most likely to expose a bug, and then exercises all possible interleavings of kernel threads around such points.
Using this instrumentation and configuration, Landslide is able to enumerate all possible interleavings of kernel threads at a granularity both fine-grained enough to expose interesting concurrency behaviour and coarse-grained enough to produce state spaces that are feasible to explore. Landslide then forces the kernel to exercise each of these interleavings, and checks for race conditions in each of them.}
When Landslide finds a bug (predicted by a set of common checks and heuristics), it stops execution and prints information about the sequence of interleavings that exposed the bug.
